Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-02 doc/JFLA2022/paper.tex
Correctly spell the name of the Goedel library.
work on Conclusion section

We have extracted part of the G\"{o}del library into a new sub-library of the Hydra-battles library: Ackermann.

@@

\TODO{General Conclusion}

@@

\subsection{Further extensions}

>>>>

We have extracted part of the Goedel library into a new sub-library of the Hydra-battles library: Ackermann.

@@

\emph{Hydra-battles} wants to be a bridge between scientific litterature (\emph{e.g.}~\cite{KP82, KS81, schutte} and proof assistant technology. For the mathematician, it may give a concrete view of the mathematical content, not only through full proofs, but also through significative computations: examples, functions associated with constructive proofs, etc. For the Coq user, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. It may be also used as a library, through opam packages.

It is also a medium sized library (more than 50K LOC), dependent on various tools and libraries of the Coq ecosystem. It may be also used to experiment new techniques of continuous maintenace of the code and its documentation.

%\TODO{General Conclusion}

@@

%\subsection{Further extensions}
